Stack Safety is a Security Property

### 2021-04-13 tex/main.tex
Pretty sure I need to merge

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
%\apt{maybe: ``Stack safety is a testable security property''?}\bcp{That
%  would sacrifice a lot of oomph for a little bit of precision, IMO.  Prefer
%  to leave it out of the title but hit it strongly in the abstract.}%
What is stack safety? The phrase is associated with a variety of compiler,
run-time, and hardware mechanisms for guarding against corruption of stack
memory.  But these mechanisms typically lack rigorous specifications,
relying instead on informal descriptions of
the safe stack manipulation behaviors that they allow
and/or specific examples of the bad behaviors that they prevent.

We propose formal criteria for stack safety, phrased in terms of
language-based security: a combination of an integrity property (``each
caller's stack frame is held invariant by the callee'') and a confidentiality
property (``the callee's behavior is insensitive to differences in the
caller's state'').
% These properties are sensible even in the presence of
% abnormal control flow.\apt{Is this important enough to mention here?}
% BCP: I think not in the abstract, but maybe in the intro.
% We further apply\apt{what does this mean? we didn't
%  invent it} a straightforward notion of
% ``well-bracketed control flow'' that restricts control flow to the
% typical pattern of matched calls and returns.
%
We argue that these criteria match common intuitions (1) by showing that
they are violated by a variety of intuitively unsafe examples and (2) by
using property-based random testing to check that appropriate variants of
the criteria are actually enforced by the stack-safety ``micro-policies''
proposed by~\citet{DBLP:conf/sp/RoesslerD18}.  Specifically, Roessler and
dehon's ``eager'' micro-policy, which catches violations as early as
possible, enforces simple ``stepwise'' versions of our confidentiality and
integrity properties, while their more performant ``lazy'' micro-policy
enforces weaker, more extensional ``observational'' variants of the
properties.

\bcp{We should mention stack data and coroutines, I think?}

% We argue \apt{do we?}\bcp{I guess we will not have time to.  Propose
%   deleting this para.} that our properties are suited to a range of other
% enforcement mechanisms. The strict stepwise properties can describe
% mechanisms that catch errors immediately, as is typical. While the
% observational properties are closely linked to lazy micro-policies they are
% weak enough to be a lower bound that captures stack safety for any
% reasonable enforcement mechanism.

\apt{This is a good story, but does it describe the paper we are able to produce this week?
  We were rejected before exactly because we claimed to have
  a general criterion, but did not in fact demonstrate its generality (which is not
  obvious). What has changed?}\bcp{I agree with these concerns. Deleted the
  para about the general story.  Does the rest now avoid making (or
  implying) claims that we can't defend?}
\bcp{Also, I think we should save
  WBCF for the intro---I can't find a way to discuss it here that is brief
  and not confusing/distracting.}

  % \ifaftersubmission\bcp{should we mention stktokens here?}
  % \leo{Not sure. We almost never cite stuff in the abstract, do we?}
  % \bcp{Some people say not to, but I think their argument is weak: I've
  %   added Nick/Andre above.  But I'm not sure we want to get into stkTokens
  %   in the abstract.}
  % \fi
\end{abstract}

@@

%% Keywords
%% comma separated list
\ifcameraready
\keywords{Stack Safety, Micro-Policies}  %% \keywords are mandatory in final camera-ready submission
\fi

@@

In this work, we take the (informal) definitions of WBCF\apt{or maybe not?}  and LSE as a starting
point, but choose a different approach to formalizing them, based on the
technical framework of language-based security~\citep{??}. We define
trace-based properties of \emph{stepwise stack integrity} and
\emph{lockstep stack confidentiality}.\apt{Could we just say ``stepwise'' for both?}
In applying these security concepts, we treat each caller as needing protection
from its callee, even as that callee may need protection from its callee in turn.
This differs from common practice in language-based security in that the
confidentiality property applies to many nested subtraces within a single execution.
\sna{How novel is this nesting?} \apt{Lost the reasoning principle that was here?}
{\em Integrity} says that a caller's local data is protected from modification by its callee,
and its {\em stepwise} interpretation formalizes this very naturally: a caller's local data
is never modified during a call. {\em Confidentiality} says that a caller's data is protected
from being leaked into its callee, and also that the callee cannot see uninitialized data.
As a reasoning principle, confidentiality guarantees that the callee's
behavior is determined only by a predictable interface that does not include the caller's
local state or the uninitialized portion of the stack. This is formalized as a
{\em noninterference}-style property that, rather than comparing pairs of whole program traces,
compares a pair of subtraces for each call, nested within other calls. The term
{\em lockstep} describes the behavior of these pairs: they step together, and any
deviation is recognized as a violation of confidentiality.
Together, these properties capture the rough intuition of LSE, but are somewhat stronger:
confidentiality contains temporal protections that LSE does not address.\apt{Maybe want to
  say a little more about this here, since it is a novelty wrt/ existing work?}

Since our stack safety occupies the same conceptual space as LSE, we should consider how it
relates to WBCF.\apt{Or maybe not. This disucssion seems too detailed for this spot in the intro.
  While it is good to note that our integrity/confidentiality properties make sense without
  WBCF-or-similar, LSE is also described independently from WBCF, so there's no novelty in that.}
First, we observe that some degree of bracketed control flow is implicit
in any notion of stack safety, simply because calls and returns must be recognizeable so
that callers and callees are distinguished. We treat control flow that creates an ambiguity between caller and
callee\apt{this is obscure}  as keeping the callee in control, and therefore such behavior can never give access
to the caller's data. An example would be if the callee attempts to ``return'' to the
wrong location, hoping to execute code on behalf of the caller: it may make the jump
without violating stack safety, but it gains no privileges on the caller's data.
Alternatively a callee might return past its immediate caller, to somewhere deeper in the
stack, and stack safety does not inherently rule this out. We therefore define WBCF as an additional
restriction \apt{on what? in what way is it formalized differently than by Skorstengaard?},
describing the standard control flow principle that a return pops exactly one frame
from the stack.
\sna{We got side-tracked a bit from talk of entry integrity, and Andrew made some good points
  about it, so let's not rule that out just yet. But I focused on returns because there's a
  clear story already.}

Part of the challenge in fully\apt{omit?} characterizing stack safety is that in a low-level machine
without built-in stacks, we are at the mercy of architectural
choices that do not relate to the abstract notion of stack safety\apt{a bit vague. what kind of choices?}.
We abstract over these choices
as much as possible, so that our model can be applied to a wide range of architectures
and enforcement mechanisms.

\apt{Intra-paragraph flow seemed awkward.}
A second challenge is
% the diversity of enforcement mechanisms APT:already implied above
enforcement mechanisms may weaken their protections that in the name of efficiency,
while arguing that they still capture stack safety in a meaningful sense.
\apt{Remainder of this paragraph might be better \emph{after} the R+DH para below.}
This calls \apt{not
  immediately obvious why. is this true for anything other than laziness?}
for an {\em extensional}
characterization of stack safety that describes the externally observable behavior
of a stack-safe system. In contract, our stepwise and lockstep properties are {\em intensional},
focusing on the internal behavior.

For example, \citet{DBLP:conf/sp/RoesslerD18} describe how to protect the stack
using tag-based \emph{micro-policies}~\citep{pump_oakland2015}.
Memory cells within each stack frame are tagged with the
identity of the function activation
that owns the frame, and access to those locations is then gated
according to the activation that is currently executing. Roessler and DeHon
explore alternative versions of this basic idea, with different ways of identifying
functions and deciding exactly which accesses are allowed.
% APT: seem repetitive:
%, to enable different ways
%of maintaining the connection between an activation identity and the memory it owns.
These vary in their efficiency and in the spatial and temporal precision of their
security guarantees.
The \emph{Depth Isolation} policy requires a strict mapping from a function
to its frame from the start of the call to its end\apt{unclear. why not simply say
  what depth is?}, and permits the function to write
only into that frame.
This seems simple and intuitively correct, but it can be expensive to implement the strict
mapping. Conversely, the \emph{Lazy Tagging and Clearing} policy improves
performance by assigning locations to the active function when they are written, which
permits  ``illicit'' writes to inaccessible stack frames so long as the
written locations are not subsequently read by their ``real'' owners. The intuitive justification
for this form of laziness is that any genuinely dangerous writes will ultimately be
detected before they can affect program behavior.

To formalize this intuition, we develop an \emph{observational integrity} property which
characterizes enforcement mechanisms that detect violations between the point when
they occur and the point when they make an observable impact. Intuitively this property
can be phrased as ``no visible reads after dangerous writes.''  We prove (in Coq) that stepwise
integrity implies observational integrity.
\sna{There is a bit of massaging old proofs to do here, and I don't recall if we
  established that this was important.\apt{medium importance. it is obvious that
    observational integerity allows behaviors that stepwise does not, but
    maybe not obvious that the converse is not true too.}}
We additionally sketch an associated {\em observational confidentiality} property
makes confidentiality extensional in the same way, although we do not know of a real
enforcement mechanism that weakens confidentiality in this way.\apt{why bother mentioning it then?}
Together, these form an {\em observational stack safety} that is highly extensional.
We therefore argue that, despite its somewhat greater complexity,
it may be a better minimal specification for
stack safety enforcement mechanisms in general.

@@

In summary, we offer the following contributions: \bcp{Section numbers are
  wonky---why just 7.1, where is 8, etc.}
\begin{itemize}
\item
  We adapt formulations of integrity and confidentiality from
  language-based security
  to formalize a parameterized {\em stepwise stack-safety property} \apt{lockstep?} and argue that
  it captures the intuitive concepts of local stack encapsulation, well-bracketed control
  flow, and temporal stack safety~(\cref{sec:lse-and-wbcf}).
\item
  We use a property-based randomized testing framework to support the claim
  that this stepwise property is actually enforced by the Depth Isolation policy
  of~\citet{DBLP:conf/sp/RoesslerD18}~(\cref{sec:conservative}).
\item
  We formalize a weaker but more extensional \emph{observational} variant of the
  stack safety property and argue that it accurately characterizes
  the Lazy Tagging and Clearing policy of~\citet{DBLP:conf/sp/RoesslerD18}
  enhanced with unique tags on each activation~(\cref{sec:lazy}).
\item
  We extend our model so that it can be instantiated in systems that pass arguments
  on the stack~(\cref{sec:??}) and in those with simple coroutines~(\cref{sec:??}).
\end{itemize}

@@

Our properties are defined in terms of an abstract machine model that makes very few
assumptions about the concrete machine that instantiates it.  We assume a register
machine with a program counter \(\PCname\) and stack pointer \(\rsp\)\apt{do we really
  need these except for WBCF?}; other
details of the machine's ISA are unimportant. We assume that we know ahead of time
the layout of memory, including where code lives and which addresses are within
the bounds of the stack.

@@

We further parameterize over the structure of the stack, particularly the means by
which a caller identifies the data that should be protected during a call. We term
this the {\em sealing convention} and model it as a relation between machine states
and addresses. From any call, those addresses that the sealing convention relates to the
state\apt{rephrased, but still obscure} will be protected until the return.

@@

We take a very strong threat model in which both caller and callee may execute
arbitrary machine code. This means that even the defender might be ill-behaved
to the point that it attempts to undermine its own protections, and we expect
enforcement mechanisms to ensure that it fails.\apt{obscure}
Hardware and timing attacks are out of scope, however.

@@

\section{Stack Safety, Intuitively}
\apt{section title is a bit sad since we're trying to convert intuition to formal spec!}
\label{sec:running-example}
\colorlet{lgray}{gray!40}
\colorlet{lred}{red!40}
\colorlet{lblue}{blue!20}

@@

%\paragraph*{Control Flow and Awkward Examples}

%\begin{figure}
%  \centering
%  \begin{minipage}{.4\textwidth}
%\begin{verbatim}
%int stash = 0;

%int main() {
%0:     int x = 1;
%1[C]:  f();
%2:     x = -x;
%3[C]:  f();
%4[R]:  return x;
%}
%\end{verbatim}
%  \end{minipage}
%  \begin{minipage}{.4\textwidth}
%\begin{verbatim}
%void f() {
%10:     if(!stash) {
%        // store return pointer
%11:       stash = $SP-1;
%12:     } else {
%13:       $SP-1 = stash;
%14:       stash = 0;
%15[R]:    return;
%        }
%}
%\end{verbatim}
%  \end{minipage}
%\label{fig:WBCF1}
%  \begin{subfigure}[t]{.4\textwidth}
%\begin{verbatim}
%int counter = 0;
%int stash = 0;
%
%int main() {
%0:     int x = 1;
%1[C]:  f();
%2:     x = -x;
%3[C]:  f();
%4[R]:  return x;
%}
%
%void f() {
%10:     switch(counter++) {
%11:       case 0:
%12[R]:      return;
%13:       case 1:
%14:         stash = $SP-1;
%15[C]:      main();
%16:         return;
%17:       default:
%18:         $SP-1 = stash;
%19[R]:      return;
%        }
%}
%\end{verbatim}
%\label{fig:WBCF2}
%  \end{subfigure}
%  \caption{Control Flow Attacks}
%  \label{fig:WBCF}
%\end{figure}

%Example \ref{fig:WBCF} shows how control flow attacks can compromise integrity in principle
%even when the attacker obeys LSE. In this case, the attacker hides a return pointer in a
%global variable and retrieves it the second time it is called, returning to the first call
%point rather than the second. A return was performed, so {\tt x} is no longer sealed, but
%line {\tt 2} is executed twice, so that {\tt main} returns 1 instead of -1.

%To prevent this, we define Well-bracketed Control Flow. Throughout the above examples, we
%have implicitly tracked the depth of the current call in order to seal memory at the correct
%depth. We also have a clear sense of where the entry points to functions are -- the top line,
%in our examples, and another instruction annotation in practice. Well-bracketed Control Flow
%holds if:

%\begin{itemize}
%\item All calls jump to entry points ({\em entry integrity})
%\item The depth counter decreases by exactly one on a return ({\em non-skipping})
%\item From a call at depth \(d\), the next state to have depth \(d\) matches the stack pointer,
%  and the program counter is at the instruction following the jal ({\em return integrity})
%\end{itemize}

%Non-skipping may seem strange -- surely the depth counter ought to decrease by one at a time
%as part of the property definition, and the problem comes when the return is to a shallower
%call's return pointer, violating return integrity? Yet some weaker enforcement mechanisms,
%such as those in which returns are implemented as invocation of a Cheri object capability,
%do allow skipping when adversarial code acts unreasonably by leaking its own return capability,
%reasoning that this is acceptable as long as only the unreasonable function is skipped
%(e.g. \citep{Skorstengaard+19b}).\apt{???} A variant of our model supports this weaker form of WBCF,
%but with tag-based policies we can enforce the non-skipping version entirely.\apt{??}
%\sna{Cite future work for details when the relevant section is finished.}

@@

\section{Randomized Testing}

@@

\section{Extension to Cheri}
\label{sec:cheri}

%\section{Extension to Software-based Enforcement}

>>>>

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
%\apt{maybe: ``Stack safety is a testable security property''?}\bcp{That
%  would sacrifice a lot of oomph for a little bit of precision, IMO.  Prefer
%  to leave it out of the title but hit it strongly in the abstract.}%
What is stack safety? The phrase is associated with a variety of compiler,
run-time, and hardware mechanisms for guarding against corruption of stack
memory.  But these mechanisms typically lack rigorous specifications;
they rely instead on informal descriptions of
the safe stack manipulation behaviors that they allow,
or specific examples of the bad behaviors that they prevent.

We propose formal criteria for stack safety, phrased in terms of
language-based security: a combination of an integrity property (``each
caller's stack frame is held invariant by the callee'') and a confidentiality
property (``the callee's behavior is insensitive to differences in the
caller's state''). We show that our properties describe the behavior of the stack-safety
``micro-policies'' of~\citet{DBLP:conf/sp/RoesslerD18}
using property-based randomized testing. An eager micro-policy
that catches violations immediately enforces our primary ``stepwise''
properties, and we define weaker, more extensional ``observational''
properties that are enforced even by a ``lazy'' micro-policy -- one
that, for performance reasons, may catch violations after they occur
but before they become visible.

These two classes of properties are interesting points along a spectrum
of notions of integrity and confidentiality. The strict stepwise properties can
describe mechanisms that catch errors immediately, the expected behavior of most
enforcement techniques. While the observational properties are closely linked to
lazy micro-policies, they also have the benefit of being highly extensional,
and therefore approaching a plausible minimum specification for stack safety in this
setting.

\apt{This is a good story, but does it describe the paper we are able to produce this week?
  We were rejected before exactly because we claimed to have
  a general criterion, but did not in fact demonstrate its generality (which is not
  obvious). What has changed?}
\sna{It's a delicate line we have to walk, because while our generality may not be
  easily demonstrable, {\em lack} of generality, as BCP pointed out, is also not
  demonstrable. So now I've just taken it out, and I'll plan to talk in the
  introduction about how we hope to be general later.}

  \ifaftersubmission\bcp{should we mention stktokens here?}
  \leo{Not sure. We almost never cite stuff in the abstract, do we?}
  \bcp{Some people say not to, but I think their argument is weak: I've
    added Nick/Andre above.  But I'm not sure we want to get into stkTokens
    in the abstract.}
  \fi
\end{abstract}

@@

%% Keywords
%% comma separated list
\keywords{Stack Safety, Micro-Policies}  %% \keywords are mandatory in final camera-ready submission

@@

In this work, we take the (informal) definition of LSE as a starting
point, but choose a different approach to formalizing it, based on the
technical framework of language-based security~\citep{??}. 
Our core properties are \emph{stepwise stack integrity} and
\emph{stepwise stack confidentiality}.
In applying these security concepts, we treat each caller as needing protection
from its callee, even as that callee may need protection from its callee in turn.
This differs from common practice in language-based security in that the
confidentiality property applies to many nested subtraces within a single execution.
\sna{How novel is this nesting?}
{\em Integrity} says that a caller's local data is protected from modification by its callee,
motivated by the reasoning principle that local data persists across a call. Its
{\em stepwise} interpretation formalizes this very naturally: a caller's local data
is never modified during a call. {\em Confidentiality} says that a caller's data is protected
from being leaked into its callee, and also that the callee cannot see uninitialized data.
As a reasoning principle, confidentiality guarantees that the callee's
behavior is determined only by a predictable interface that does not include the caller's
local state or the uninitialized portion of the stack. This is formalized as a
{\em noninterference}-style property that, rather than comparing pairs of whole program traces,
compares a pair of subtraces for each call, nested within other calls. Once again
{\em stepwise} describes the granularity of enforcement: at every step of a call,
changes in the state are independent of the caller's data.

Together, these properties capture the rough intuition of LSE, but are somewhat stronger.
First, we model returns as returns to a valid return target; an invalid return
is treated as a mere jump within the callee, and does not grant access to the caller's
data. So, even without WBCF, our stack safety properties rule out many control flow attacks.
The attacker in such an instance is permitted to ``return'' so long as it avoids
violating the integrity and confidentiality of the caller. Second, confidentiality
contains temporal protections that LSE does not implicitly address.
\apt{Maybe want to say a little more about this here, since it is a novelty wrt/ existing work?}
\sna{TODO: Say a little more, but make sure it's accurate first.}

One challenge in characterizing stack safety is that in a low-level machine
without built-in stacks, we are at the mercy of architectural
choices that do not relate to the abstract notion of stack safety. Some implementations
may have only a stack pointer while others add a frame pointer, in some systems return
addresses and data live in separate stacks, and so on. We abstract over these choices
as much as possible, so that our model can be applied to a wide range of architectures
and enforcement mechanisms.

A second challenge is that
enforcement mechanisms may weaken their protections that in the name of efficiency,
while arguing that they still capture stack safety in a meaningful sense.
For example, \citet{DBLP:conf/sp/RoesslerD18} describe how to protect the stack
using tag-based \emph{micro-policies}~\citep{pump_oakland2015}.
Memory cells within each stack frame are tagged with the
identity of the function activation
that owns the frame, and access to those locations is then gated
according to the activation that is currently executing. Roessler and DeHon
explore alternative versions of this basic idea, with different ways of identifying
functions and deciding exactly which accesses are allowed.
These vary in their efficiency and in the spatial and temporal precision of their
security guarantees.
The \emph{Depth Isolation} policy prevents a callee from writing outside its frame
at all, which is simple and intuitively correct, but it must manually clear the tags
on the frame on each return, which is very expensive. Conversely, the
\emph{Lazy Tagging and Clearing} policy improves
performance by assigning locations to the active function when they are written, which
permits  ``illicit'' writes to inaccessible stack frames so long as the
written locations are not subsequently read by their ``real'' owners. Intuitively,
this form of laziness is justified if any dangerous writes will
ultimately be detected before they can affect program behavior.

But what does ``affecting program behavior'' really mean? This micro-policy
calls for a second characterization of stack safety in terms of the externally
observable behavior of a stack-safe system. Such a characterization will have the
additional benefit of being more {\em extensional}, concerned primarily with the
external behavior of the system. In contract, our stepwise properties are {\em intensional},
focusing on internal details that may not actually matter to overall security.

To formalize this intuition, we develop an \emph{observational integrity} property which
characterizes enforcement mechanisms that detect violations between the point when
they occur and the point when they make an observable impact. Intuitively this property
can be phrased as ``no visible reads after dangerous writes.''  We prove (in Coq) that stepwise
integrity implies observational integrity.
\sna{There is a bit of massaging old proofs to do here, and I don't recall if we
  established that this was important.\apt{medium importance. it is obvious that
    observational integerity allows behaviors that stepwise does not, but
    maybe not obvious that the converse is not true too.}}
We additionally sketch an associated {\em observational confidentiality} property
makes confidentiality extensional in the same way, although we do not know of a real
enforcement mechanism that weakens confidentiality in this way.
\apt{why bother mentioning it then?}
\sna{If a relatively extensional characterization is a worthwhile contribution
  in its own right, then it's worth mentioning that we have one. If not, then indeed,
  we shouldn't mention it -- or get too excited about extensionality in general, because
  lockstep isn't extensional.}
Together, these form an {\em observational stack safety} that is highly extensional.
We therefore argue that, despite its somewhat greater complexity,
it may be a better minimal specification for
stack safety enforcement mechanisms in general.

@@

In summary, we offer the following contributions: \bcp{Section numbers are
  wonky---why just 7.1, where is 8, etc.}
\begin{itemize}
\item
  We adapt formulations of integrity and confidentiality from language-based security
  to formalize a parameterized {\em stepwise stack-safety} property and argue that it
  captures the intuitive concepts of stack safety~(\cref{sec:lse}). Our model extends to
  argument passing on the stack and to a simple coroutine system.
\item
  We use a property-based randomized testing framework to support the claim
  that this stepwise property is actually enforced by the Depth Isolation policy
  of~\citet{DBLP:conf/sp/RoesslerD18}~(\cref{sec:testing}).
\item
  We formalize a weaker but more extensional \emph{observational} variant of the
  stack safety property and argue that it accurately characterizes
  the Lazy Tagging and Clearing policy of~\citet{DBLP:conf/sp/RoesslerD18}
  enhanced with unique tags on each activation~(\cref{sec:lazy}).
\end{itemize}

@@

Our properties are defined in terms of an abstract machine model that makes very few
assumptions about the concrete machine that instantiates it.  We assume a register
machine with a program counter \(\PCname\); other
details of the machine's ISA are unimportant. We assume that we know ahead of time
the layout of memory, including where code lives and which addresses are within
the bounds of the stack.

@@

We further parameterize over the structure of the stack, particularly the means by
which a caller identifies the data that should be protected during a call. We term
this the {\em sealing convention}, which maps a machine state to a set of addresses.
If a state's \(\PCname\) is annotated as a call, the sealing convention tells us
which addresses must be protected until the return.

@@

We take a very strong threat model in which both caller and callee may execute
arbitrary machine code. Hardware and timing attacks are out of scope, however.

@@

\section{Demonstrating Stack Safety}
\label{sec:running-example}
\colorlet{lgray}{gray!40}
\colorlet{lred}{red!40}
\colorlet{lblue}{blue!20}

@@

\paragraph*{Control Flow Attacks}
\begin{figure}
  \centering
  \begin{minipage}{.4\textwidth}
\begin{verbatim}
int *stash = 0;

int main() {
0:     int x;
1:     x = 1;
2[C]:  f();
3:     x = -x;
4[C]:  f();
5[R]:  return x;
}

void f() {
10:     if(!stash) {
        // store return pointer
11:       stash = $SP-1;
12:     } else {
13:       $SP-1 = stash;
14:       stash = 0;
        }
15[R]:    return;
}
\end{verbatim}
  \end{minipage}
\label{fig:controlflow}
 %  \begin{subfigure}[t]{.4\textwidth}
 %\begin{verbatim}
 %int counter = 0;
@@ -1194,42 +1090,43 @@ the program counters will differ, breaking the lockstep.
 %\end{verbatim}
 %\label{fig:WBCF2}
 %  \end{subfigure}
-%  \caption{Control Flow Attacks}
-%  \label{fig:WBCF}
-%\end{figure}
+  \caption{Control Flow Attacks}
+  \label{fig:WBCF}
+\end{figure}

@@

\section{Randomized Testing}
\label{sec:testing}

@@
